Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
LOTS OF ENGLISH SENTENCES

\newcommand{\eqvDS}[3]{#2 \approx_{\mathcal{DS}} #3}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
		\sOOreturn{u}{\kappa}
		\\ &
	}{
		\sidecond{applyCast(c,v) = \rOOsucc{u}}
	}

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
		\sOOhalt{(\oOOblame{l})}
		\\ &
	}{
		\sidecond{applyCast(c,v) = \rOOfail{l}}
	}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}
	\end{array}
	\]

@@

\begin{proposition}[\lazyD\ hypercoercion is a monoid]
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}

@@

	\caption{Space-efficient CEK machine $ \mathcal{S}(C) $}
	\label{machine-cekcc}
\end{figure}
 (in the style of CEK machines)
\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
machine is similar to \ineffCEK{}. 
The most important differences are in values and continuations.
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

Let $ v $ range over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pre-continuation capped with a cast.
Pre-continuation are like the continuations in \ineffCEK.

@@

\todo[inline]{Give a high-level summary of the proof.
	The summary should be enough so that the reader knows a bit
	about why you introduce the various definitions below. -JS}
\todo[inline]{KC needs to move some content in the next section to here. -KC}

The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of \ineffCEKD. Exceptions include the relations from 
continuations to pre-continuations, between continuations, and between values. 
We omit subscripts when there is no ambiguity.

\todoKC{write down the exceptional bisimilarity relations}

\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and \ineffCEKD]
	\label{thm:surely-monoidic-reduce}
	For all cast representations $ C $, 
	if $ C $ is surely \lazyD{} and monoidic,
	$ s_1 \in \text{\ineffCEKD} $,
	$ s_2 \in \mathcal{S}(C) $, and
	$ s_1 \approx s_2 $, 
	\begin{enumerate}
		\item If $ \judgeDreduce{s_1}{s_3} $,
		then
		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
		such that \begin{itemize}
			\item $ s_5 \approx s_4 $, and
			\item $ \judgeSreduce{C}{s_2}{s_4} $,
			\item $ \judgeDreduceTrans{s_3}{s_5} $
		\end{itemize}
		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
		then
		there exist $ s_3 \in \mathcal{C} $,
		such that \begin{itemize}
			\item $ s_3 \approx s_4 $
			\item $ \judgeDreduceTrans{s_1}{s_3} $
		\end{itemize}
	\end{enumerate}
\end{lemma}
\begin{proof}
	See the supplementary material.
\end{proof}

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeDeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
	\todo[inline]{I'm guessing that you prove this lemma by induction,
		using Lemma~\ref{thm:surely-monoidic-reduce}.
		Proofs by induction are not ``immediate''. -JS}
\end{proof}

@@

With the properties of surely \lazyD{} cast representation, it is 
straightforward to proof that 
all machines instantiated with these cast representations bisimulate each 
other. 
The bisimulation relation of states ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states.
\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
	``bisimulation relation''. I don't think you are using it properly
	in the above sentence. -JS
	\\---\\
	Fixed.
	I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' 
	from 
	wikipedia. (https://en.wikipedia.org/wiki/Bisimulation).
	-KC}
We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

The relations between continuations, pre-continuations, enviroments, values, 
cast results are also derived from their definitions. But the relation for 
casts is special: \begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
		\item $ s_2 \approx s_4 $ and
		\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{lemma}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} cast representation, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD\ cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	Immediately from Lemma~\ref{thm:CEKS-bisim}.
\end{proof}

\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
	$ \mathcal{C}_\mathtt{D} $]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}.
\end{proof}

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct.

To use hypercoercion as a 
cast representation in our framework, we need to defined four functions: $ 
cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
define the $ applyCast(c,v) $  in \figref{hc-applyCast}

Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
shallow-consistency to compare middles and values ($ m \smile v $) in the 
natural way.

@@

\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

>>>>

\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
\begin{cases}
	\sOOreturn{u}{\kappa} & \sidecond{applyCast(c,v) = \rOOsucc{u}}
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(c,v) = \rOOfail{l}}
\end{cases}
	}{}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}

\redrule{
\sOOhalt{o}}{
\sOOhalt{o}}{}
	\end{array}
	\]

@@

\begin{proposition}[\lazyD\ hypercoercion is a monoid]
	\label{thm:hc-monoid}
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}

@@

	\caption{Space-efficient CEK machine $ \mathcal{S}(C) $}
	\label{machine-cekcc}
\end{figure}
\figref{machine-cekcc} defines, \effCEK{C}, a space-efficient semantics of cast 
calculus in the style of CEK machines.
This machine is similar to \ineffCEK{}. 
The most important differences are in values and continuations.
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

Let $ v $ range over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pre-continuation prefixed with a cast.
Pre-continuation are like the continuations in \ineffCEK.

@@

\todo[inline]{Give a high-level summary of the proof.
	The summary should be enough so that the reader knows a bit
	about why you introduce the various definitions below. -JS
\\---\\
Fixed -KC}

In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD and 
is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
$. We proof this theorem with a weak bisimulation between \ineffCEKD\ and 
\effCEK{C}.

The bisimulation relation between states ($\eqvSD{C}{s}{s}$) is mostly derived 
from the state definition: \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

The bisimulation relation between environments and cast results are derived 
from their definitions as well. And the relation from continuations in 
\ineffCEKD\ and the pre-continuation in \effCEK{C} is in the natural way, for 
example: \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\kOOconsI{e}{\rho_1}{\kappa_1} \approx \kOOconsI{e}{\rho_2}{\kappa_2}
}
\end{gather*}

And the relation between continuations is defined in terms of $ cont(k) $ and $ 
ext(c,k) $: \begin{gather*}
\inference{
	k \approx \kappa
}{
	cont(k) \approx \kappa
}
\quad
\inference{
	\kappa_1 \approx \kappa_2
}{
	ext(cast(T_1,l,T_2),\kappa_1)
	\approx
	\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2} 
}
\end{gather*}

The relation between values is more special. When the \ineffCEKD\ value is 
non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
the cast into the value constructors, except injections. For examples: 
\begin{gather*}
\inference{
	v_1, v_2 : P &
	v_1 \approx v_2
}{
	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
}
\quad
\inference{
	\Gamma , x : T_1 \vdash T_2 &
	\rho_1 \approx \rho_2
}{
	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
}
%\quad
%\inference{
%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
%	\approx
%	v
%}{
%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
%}
\\
\inference{
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
}{
	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
	\approx
	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
}
\end{gather*}

Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
introduce one more definition: $ s_1 \approx^{*} s_2 $ if and only if there 
exists $ s_2' \in \text{\ineffCEKD} $ 
such that $ \judgeCreduceTrans{s_2}{s_2'}$ and $ s_1 \approx s_2' $.

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
	\label{thm:surely-monoidic-reduce}
	For all cast representations $ C $, 
	if $ C $ is surely \lazyD{} and is a monoid, 
	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
	$ s_{2}, s_{2}' \in \text{\ineffCEKD} $,
	$ s_{1} \approx s_{2} $,
	$ \judgeSreduce{C}{s_{1}}{s_{1}'} $, and
	$ \judgeDreduce{s_{2}}{s_{2}'} $, then
%	then there exist $ s_2'' \in \text{\ineffCEKD} $ such that
	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
%	\begin{enumerate}
%		\item If $ \judgeDreduce{s_1}{s_3} $,
%		then
%		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
%		such that \begin{itemize}
%			\item $ s_5 \approx s_4 $, and
%			\item $ \judgeSreduce{C}{s_2}{s_4} $,
%			\item $ \judgeDreduceTrans{s_3}{s_5} $
%		\end{itemize}
%		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
%		then
%		there exist $ s_3 \in \mathcal{C} $,
%		such that \begin{itemize}
%			\item $ s_3 \approx s_4 $
%			\item $ \judgeDreduceTrans{s_1}{s_3} $
%		\end{itemize}
%	\end{enumerate}

Or diagrammatically, 
\[\begin{array}{clclc}
s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
\rotatebox[origin=c]{90}{$\approx$} 
& & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
s_{2} & 
\longrightarrow_{\text{\ineffCEKD}} & s_2' &
\longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
\end{array}\]

\end{lemma}
\begin{proof}
	By following the transition rule of \ineffCEKD. See the supplementary 
	materials for details.
\end{proof}

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and is a monoid,
	\[
	\judgeSeval{C}{e}{o}
	 \; \text{if and only if} \; 
	\judgeDeval{e}{o}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
	\todo[inline]{I'm guessing that you prove this lemma by induction,
		using Lemma~\ref{thm:surely-monoidic-reduce}.
		Proofs by induction are not ``immediate''. -JS
	\\---\\Fixed. -KC}
\end{proof}

@@

In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD, then 
$ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first prove 
that all $ S(C) $ where $ C $ is surely lazyD are equivalent, then connect this 
theorem to Lemma~\ref{thm:surely-monoidic-eval}.

We prove the equivalence among \effCEK{S(C)} with strong bisimulation. This 
time almost all the bisimulation relations are all derived from definitions 
except the relaton for casts, which is by cast constructors:
\begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
	$ s_1 \approx s_2 $,
	$ \judgeSreduce{C_1}{s_1}{s_1'} $, and
	$ \judgeSreduce{C_2}{s_2}{s_2'} $, then 
	$ s_1' \approx s_2' $

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
	This proof is effectively a duplication of the transition rule of 
	\effCEK{S(C)}.
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} cast representation, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD\ cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
\end{proof}

\begin{theorem}[Surely \lazyD\ Cast Representations Respect \ineffCEKD]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	If we have a surely LazyD cast representation and it is a monoid, this 
	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
	represent casts as a list of triples of type, label, and type, where $ 
	id(T) $ is the empty list and $ seq(c,c,) $ is list append. Another such 
	representation is the \lazyD\ hypercoercion!
\end{proof}

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct. First we define $ applyCast(c,v) $ to make it a cast representation, 
then prove that it is surely lazyD, and finally apply 
Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.

%To use hypercoercion as a 
%cast representation in our framework, we need to defined four functions: $ 
%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
%we 
%define the $ applyCast(c,v) $  in

\figref{hc-applyCast} defines $ applyCast(c,v) $ for \lazyD\ hypercoercion. 
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
shallow-consistency to compare middles and values ($ m \smile v $) in the 
natural way.

@@

\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Theorem~\ref{thm:surely-lazyD-correct} and 
	Lemma~\ref{thm:hc-surely-lazyD}.
	Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}
